---
title: "Using Quarto to share and publish your research"
author: "David Mawdsley"
date: 1 September 2022
format: revealjs
jupyter: python3 
---

```{r}
library(tidyverse)
library(plotly)
```


## Overview 

- What is Quarto?
- Advantages over Jupyter notebooks
- Output formats
- Demo

## What is Quarto?

- Combine text content and executable code into:
  - Presentations (e.g. this :-)
  - Websites
  - Journal articles
  - Books
- Supports multiple languages
  - Python
  - R
  - Julia
  


## What is Quarto? (2)

- Supports multiple output formats:
  - PDF
  - HTML
  - Word (`.docx`)
  - Powerpoint (`.pptx`)
  - epub

## Benefits over Jupyter notebooks

- Can produce anything between:
  - All text, hidden code (i.e. a paper, a web page)
  - All the code visible (i.e. a Jupyter notebook)
- `.qmd` document is human readable
  - Markdown and code delimiters
  - Results are not embedded in the `.qmd` document; only in the output
  - no chunks of unreadable json
  - Works better with version control

## Risks/Issues

- New technology
  - Version 1 released July 2022
  - Was in beta for a long while

## Demo 

This presentation is written using Quarto

Here is some R code, showing the code:

```{r, echo=TRUE}
1 + 1
```

And without

```{r}
1 + 1
```

## Graphs

```{r}
g <- mtcars %>% 
  ggplot(aes(x = wt, y = mpg, colour = as.factor(cyl))) + 
  geom_point()
print(g)
```

## Interactive graphs

Using [Plotly](https://plotly.com/r/)

```{r}
plotly::ggplotly(g)

```



## Python

Can do the same with Python:


```{python}
#| echo: true
1 + 1
```

Or just the results:

```{python}
1 + 1
```


## Graphs

Using matplotlib

```{python}
import numpy as np
import matplotlib.pyplot as plt

# Fixing random state for reproducibility
np.random.seed(19680801)


N = 50
x = np.random.rand(N)
y = np.random.rand(N)
colors = np.random.rand(N)
area = (30 * np.random.rand(N))**2  # 0 to 15 point radii

plt.scatter(x, y, s=area, c=colors, alpha=0.5)
plt.show()
```


## Plotly

```{python}
import plotly.express as px

fig = px.scatter(x, y)

fig.show()

```



